```{r, echo=FALSE, include=FALSE}
## Get VERSION and create file names
ver <- sub(x=grep(x=readLines("DESCRIPTION"), pattern="^Version: ",
                  value=TRUE),
           pattern="^Version: ", replacement="")
pkg.name <- "legtheme_"
pkg.source <- paste0(pkg.name, ver, ".tar.gz")
pkg.win <- paste0(pkg.name, ver, ".zip")
```

# legtheme `r ver`

[![Build Status](https://travis-ci.org/leg-ufpr/legtheme.svg?branch=master)](https://travis-ci.org/leg-ufpr/legtheme)

LEG template for documents.

## Usage

After installing (sse below), you can create a draft document from one
of the themes available:

- `beamer_leg` is a theme for beamer slides
- `proj_generico` is a theme for a generic project or any other similar
  document in PDF

To create a draft for `beamer_leg` use:

```{r, eval=FALSE}
library(rmarkdown)
draft(file = "slides.Rmd", template = "beamer_leg",
      package = "legtheme", create_dir = FALSE, edit = FALSE)
```
This will create (in the current directory) a file named `slides.Rmd`
which can be further rendered with

```{r, eval=FALSE}
render("slides.Rmd")
```

Similarly, to create a draft document for the `proj_generico` theme,
just use:

```{r, eval=FALSE}
draft(file = "proj.Rmd", template = "proj_generico",
      package = "legtheme", create_dir = FALSE, edit = FALSE)
render("proj.Rmd")
```

## Download and install

The easiest way to install is directly from this repository with the
**remotes** (or **devtools**) packages

```{r, eval=FALSE}
remotes::install_github("leg-ufpr/legtheme")
```

In any case, there are detailed instructions below for different
plataforms.

### Linux/Mac

Use the `remotes` package (available from
[CRAN](http://cran-r.c3sl.ufpr.br/web/packages/remotes/index.html)) to
install automatically from this GitHub repository:

```{r, eval=FALSE}
library(remotes)
install_github("leg-ufpr/legtheme")
```

Alternatively, download the package tarball: [`r pkg.source`][]
and run from a UNIX terminal (make sure you are on the container file
directory):

```{r, echo=FALSE, comment=NA}
cmd <- paste("R CMD INSTALL -l /path/to/your/R/library", pkg.source)
cat(cmd, sep = "\n")
```

Or, inside an `R` session:

```{r, echo=FALSE, comment=NA}
inst <- paste0("install.packages(", "\"", pkg.source, "\"", ", repos = NULL,\n",
               "                 lib.loc = \"/path/to/your/R/library\",\n",
               "                 dependencies = TRUE)")
cat(inst, sep = "\n")
```

Note that `-l /path/to/your/R/library` in the former and `lib.loc =
"/path/to/your/R/library"` in the latter are optional. Only use it if
you want to install in a personal library, other than the standard R
library.

### Windows

Download Windows binary version: [`r pkg.win`][] (**do not unzip
it under Windows**), put the file in your working directory, and from
inside `R`:

```{r, echo=FALSE, comment=NA}
instw <- paste0("install.packages(", "\"", pkg.win, "\"", ", repos = NULL,\n",
                "                 dependencies = TRUE)")
cat(instw, sep = "\n")
```

## Authors

- Original [theme](https://github.com/coatless/uiucthemes)
  (`uiucthemes`) by [James L. Balamuta](https://github.com/coatless)
- LEG theme adaptation by:
  - [Fernando de Pol Mayer][]

## Documentation

The reference manual in PDF can be found here: [legtheme-manual.pdf][]

## License

MIT. See [LICENSE](./LICENSE)

<!-- links -->

```{r, echo=FALSE, include=FALSE}
pkg.source.link <- paste0(
    "https://github.com/leg-ufpr/legtheme/raw/master/downloads/",
    pkg.source)
pkg.win.link <- paste0(
    "https://github.com/leg-ufpr/legtheme/raw/master/downloads/",
    pkg.win)
```

[`r pkg.source`]: `r pkg.source.link`
[`r pkg.win`]: `r pkg.win.link`
[legtheme-manual.pdf]: https://github.com/leg-ufpr/legtheme/raw/master/downloads/legtheme-manual.pdf
[Fernando de Pol Mayer]: http://www.leg.ufpr.br/~fernandomayer
